---
title: 'London Crime Statistics'
author: "Lena Nguyen"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## About the dataset

I am going to explore the public dataset about crime in London available on [BigQuery](https://console.cloud.google.com/marketplace/details/greater-london-authority/london-crime). This dataset includes data about crimes that occurred by different geographic levels from 2008 until present. I ran a query to get the data about different types of crimes committed in each borough for each month from 2008 until present and downloaded that data into a csv.

First, let's load the data.

```{r load_data}
crime <- read_csv('ldn_crime.csv')
```

## Types of Crime

First, let's look at the big picture and see what are the most common types of crime committed in London. 

```{r type_city, echo=FALSE}
# change dataset for plot
total_crime <- crime %>% 
  group_by(major_category) %>% 
  summarise(total = sum(num_crime)) %>%
  mutate(percentage = round(total / sum(total), digits = 4))

# Make bar plot
ggplot(total_crime, 
       aes(x = reorder(major_category, percentage), y = percentage)) + 
  geom_col(fill = "#037ac4") +
  geom_text(aes(label = scales::percent(percentage),
                y= percentage), nudge_y = 0.035, size = 3.5) +
  coord_flip() +
  labs(title = 'Types of crime commited in London (2008-2016)',
       y = 'Percent of all crimes committed') +
  scale_y_continuous(limits = c(0,0.5), 
                     expand = c(0,0), 
                     labels = scales::percent_format(accuracy = 1)) +
  theme(
    axis.title.x = element_text(size = 10, face = 'bold'),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    plot.title = element_text(face = 'bold'),
    plot.margin = unit(c(0.5,0.5,0.5,0.5), 'cm')
  )
```

