---
title: 'London Crime Statistics (2008 - 2016)'
output: 
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE)

library(tidyverse)
```

### About the dataset

I am going to explore the public dataset about crime in London available on [BigQuery](https://console.cloud.google.com/marketplace/details/greater-london-authority/london-crime). This dataset includes data about crimes that occurred by different geographic levels from 2008 until 2016. I ran a query to get the data about different types of crimes committed in each borough for each month from 2008 until 2016 and downloaded that data into a csv.

First, let's load the data.

```{r load_data}
crime <- read_csv('ldn_crime.csv')
```

### Does the number of crime committed vary by year?

First, let's look at how much crime is committed in total in London over the years. There is a slight decrease in the number of incidents in 2013 and 2014 but overall, the level of crime in London has remained about the same over those 8 years.

```{r type_borough}
# change dataset for plot
crime %>% 
  group_by(year) %>% 
  summarise(total = sum(num_crime)) %>%
  ggplot(aes(x = year, y = total)) +
  geom_col(fill = '#037ac4') +
  scale_y_continuous(limits = c(0,800000), expand = c(0,0), 
                     labels = scales::comma) +
  scale_x_discrete(limits = 2008:2016, expand = c(0,0)) +
  labs(x = 'Year', y = 'Total Number of Incidents') +
  theme(
    axis.title = element_text(size = 10, face = 'bold'),
    axis.ticks.y = element_blank()
  )
```

### What types of crime are committed in London?

Now let's see what are the most common types of crime committed in London from 2008-2016. In the chart below, we can see that the most common type of crime committed in London is theft and handling (41.3% of all crimes committed). 

```{r type_city, echo = FALSE}
# change dataset for plot
crime %>% 
  group_by(major_category) %>% 
  summarise(total = sum(num_crime)) %>%
  mutate(percentage = round(total / sum(total), digits = 4)) %>%
  # Make bar plot
  ggplot(aes(x = reorder(major_category, percentage), y = percentage)) +
  geom_col(fill = "#037ac4") +
  geom_text(aes(label = scales::percent(percentage),
                y= percentage), nudge_y = 0.035, size = 3.5) +
  coord_flip() +
  labs(y = 'Percent of all crimes committed') +
  scale_y_continuous(limits = c(0,0.5), 
                     expand = c(0,0), 
                     labels = scales::percent_format(accuracy = 1)) +
  theme(
    axis.title.x = element_text(size = 10, face = 'bold'),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    plot.title = element_text(face = 'bold'),
    plot.margin = unit(c(0.5,0.5,0.5,0.5), 'cm')
  )
```

