---
title: 'London Crime Statistics'
author: "Lena Nguyen"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## About the dataset

I am going to explore the public dataset about crime in London available on [BigQuery](https://console.cloud.google.com/marketplace/details/greater-london-authority/london-crime). This dataset includes data about crimes that occurred by different geographic levels from 2008 until present. I ran a query to get the data about different types of crimes committed in each borough for each month from 2008 until present and downloaded that data into a csv.

First, let's load the data.

```{r load_data}
crime <- read_csv('ldn_crime.csv')
```

## Types of Crime

First, let's look at the big picture and see what are the most common types of crime committed in London. 

```{r type_city, echo=FALSE}
# change dataset for plot
total_crime <- crime %>% 
  group_by(major_category) %>% 
  summarise(total = sum(num_crime)) %>%
  mutate(percentage = round(total / sum(total), digits = 4))

# Make bar plot
ggplot(total_crime, 
       aes(x = reorder(major_category, percentage), y = percentage)) + 
  geom_col(fill = "#037ac4") +
  geom_text(aes(label = scales::percent(percentage),
                y= percentage), nudge_y = 0.035, size = 3.5) +
  coord_flip() +
  labs(x = 'Type of crime', y = 'Percent of total crime committed') +
  scale_y_continuous(limits = c(0,0.5), labels = scales::percent) +
  theme(
    axis.title = element_text(size = 10, face = "bold"),
    axis.ticks.y = element_blank()
  )
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
